\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{longtable}
\usepackage[margin=0.2in]{geometry}
\begin{document}

\begin{longtable}[width=\pagewidth]{@{}llp{6cm}l@{}}
\textbf{Date} & \textbf{Iteration} & \textbf{Changes} &
\textbf{Author}\tabularnewline
\endhead
2018-02-27 & First delivery. (Sprint \#0) & None. Initial document. &
\emph{Shared Effort}\tabularnewline
2018-03-09 & Sprint \#1 & Improve non-functional requirements. &
Wiebe-Marten Wijnja\tabularnewline
2018-03-09 & Sprint \#1 & Added enabling/disabling monitoring of
specific endpoints to nice to haves. & Tom Apol\tabularnewline
2018-03-12 & Sprint \#1 & Updated the \emph{flask-monitoring-dashboard}
API specification to the latest version. & Koen Bolhuis\tabularnewline
2018-03-23 & Sprint \#2 & Made changes based on TA suggestions. & Jeroen
Langhorst\tabularnewline
2018-04-16 & Sprint \#3 & Added frontend and other backlog. & Lars
Doorenbos\tabularnewline
\begin{minipage}[t]{0.22\columnwidth}\raggedright
2018-04-17\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
Sprint \#3\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
Updated backlog formatting.

Added backend tasks to the backlog.

Updated \emph{flask-monitoring-dashboard} API specification to the
latest version.\strut
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedright
Koen Bolhuis\strut
\end{minipage}\tabularnewline
2018-04-23 & Sprint \#4 & Updated most of Patricks comments. & Lars
Doorenbos\tabularnewline
2018-04-28 & Sprint \#4 & Updated backlog. & Lars
Doorenbos\tabularnewline
2018-04-28 & Sprint \#4 & Updated dashboard requirements. & Jeroen
Langhorst\tabularnewline
2018-04-28 & Sprint \#4 & Moved sending emails (for email verification)
to Sprint \#5 in the backlog, since it takes a lot of work to implement
and test. & Koen Bolhuis\tabularnewline
2018-05-14 & Sprint \#5 & Added finished backlog & Lars
Doorenbos\tabularnewline

\end{longtable}



\end{document}
